\section*{Legal notice to Investors}\addcontentsline{toc}{section}{Legal notice to Investors}

\textbf{IMPORTANT NOTICES}

\medskip

The AppCoins are not securities or units in a collective investment scheme or business trust, each as defined under Singapore's Securities and Futures Act (Cap. 289) (\textbf{"SFA"}). Accordingly, the SFA does not apply to the offer and sale of the AppCoins. For the avoidance of doubt, this initial offering of AppCoins need not be accompanied by any prospectus or profile statement and no prospectus or profile statement needs to be lodged with the Monetary Authority of Singapore (\textbf{"MAS"}).

\medskip

This White Paper does not constitute an offer of, or an invitation to purchase, the AppCoins in any jurisdiction in which such offer or sale would be unlawful. No regulatory authority in Singapore, including the MAS, has reviewed or approved or disapproved of the AppCoins or this White Paper. This White Paper and any part hereof may not be distributed or otherwise disseminated in any jurisdiction where offering tokens in the manner set out this White Paper is regulated or prohibited.

\medskip

The information in this White Paper is current only as of the date on the cover hereof. For any time after the cover date of this White Paper, the information, including information concerning Aptoide's business operations and financial condition may have changed. Neither the delivery of this White Paper nor any sale made in the related initial token offering shall, under any circumstances, constitute a representation that no such changes have occurred. Aptoide does not make or purport to make, and hereby disclaims, any representation, warranty, undertaking, or other assurance in any form whatsoever to any person, including any representations, warranties, undertakings, or other assurances in relation to the truth, accuracy, or completeness of any part of the information in this White Paper.

\medskip

Whether taken as a whole or read in part, this White Paper is not, and should not be regarded as, any form of legal, financial, tax, or other professional advice. You should seek independent professional advice before making your own decision as to whether or not to purchase any AppCoins. You are responsible for any and all evaluations, assessments, and decisions you make in relation to investing in the AppCoins. You may request for additional information from Aptoide in relation to this offer of AppCoins. Aptoide may, but is not obliged to, disclose such information depending on whether (i) it is legal to do so and (ii) the requested information is reasonably necessary to verify the information contained in this White Paper.

\medskip

AppCoins are intended for use within applications available on the Aptoide App Store for purposes including purchasing in-application items and serving as a medium of in-application advertising revenue, and Aptoide warrants that the AppCoins are fit for these purposes. However, Aptoide is not responsible for compelling any person to accept AppCoins and disclaims, to the fullest extent permitted by law, all liability for any adverse consequences arising out of or in relation to such rejections of AppCoins.

\medskip

Upon purchasing any AppCoins, you will be deemed to have reviewed this White Paper (and any information requested and obtained from Aptoide) in full and to have agreed to the terms of this offering of AppCoins, including to the fact that this offering does not fall within the scope of any securities laws in Singapore and is not regulated by the MAS. You further acknowledge and agree that the AppCoins are not securities and are not meant to generate any form of investment return.

\medskip

The AppCoins and related services provided by Aptoide (if any) are provided on an "as is" and "as available" basis. Aptoide does not grant any warranties or make any representation, express or implied or otherwise, as to the accessibility, quality, suitability, accuracy, adequacy, or completeness of the AppCoins or any related services provided by Aptoide, and expressly disclaims any liability for errors, delays, or omissions in, or for any action taken in reliance on, the AppCoins and related services provided by Aptoide. No warranty, including the warranties of non-infringement of third party rights, title, merchantability, satisfactory quality, or fitness for a particular purpose, is given in conjunction with the AppCoins and any related services provided by Aptoide.

\medskip
\medskip

\textbf{RISK FACTORS}

\medskip

\textit{Regulatory risks}\\
The regulation of tokens such as the AppCoins is still in a very nascent stage of development in Singapore. A high degree of uncertainty as to how tokens and token-related activities are to be treated exists. The applicable legal and regulatory framework may change subsequent to the date of issuance of this White Paper. Such change may be very rapid and it is not possible to anticipate with any degree of certainty the nature of such regulatory evolution. Aptoide does not in any way represent that the regulatory status of the AppCoins will remain unaffected by any regulatory changes that arise at any point in time before, during, and after this offering.

\medskip

\textit{No regulatory supervision}\\
None of Aptoide or its affiliates is currently regulated or subject to the supervision of any regulatory body in Singapore. In particular, Aptoide and its affiliates are not registered with MAS in Singapore as any type of regulated financial institution or financial advisor and are not subject to the standards imposed upon such persons under the Securities and Futures Act, Financial Advisors Act, and other related regulatory instruments. Such persons are required to comply with a variety of requirements and standards concerning disclosures, reporting, compliance, and conduct of their operations for purposes or maximising investor protections. Since Aptoide is not subject to such requirements or standards, it will make decisions on those issues at its own discretion. While Aptoide will have regard to best practices on these issues, holders of AppCoins may not necessarily enjoy the same extent and degree of investor protections as would be the case should they invest with regulated entities instead.

\medskip

\textit{No fiduciary duties owed}\\
As Aptoide is not a regulated financial institution, it does not owe investors in AppCoins any fiduciary duties. This means that Aptoide has no legal obligation to always act in good faith in the best interests of holders of AppCoins. While Aptoide will have regard to the interests of holders of AppCoins, it is also permitted to consider the interests of other key stakeholders and to prefer these interests over the interests of AppCoins holders. This may mean that Aptoide is permitted to make decisions that conflict with the interests of AppCoins holders. Not owing any fiduciary duties to holders of AppCoins also means that holders of AppCoins may have limited rights of recourse against Aptoide and its affiliates in the event of disputes.

\medskip

\textit{Tax risks}\\
The tax characterisation of AppCoins is unclear. Accordingly, the tax treatment to which they will be subject is uncertain. All persons who wish to purchase AppCoins should seek independent tax advice prior to deciding whether to purchase any AppCoins. Aptoide does not make any representation as to whether any tax consequences may arise from purchasing or holding AppCoins.

\medskip

\textit{Risks from third parties}\\
The tokenised nature of AppCoins means that they are a blockchain-based asset. The security, transferability, storage, and accessibility of blockchain assets depends on factors outside of Aptoide's control, such as the security, stability, and suitability of the underlying blockchain (in this case, the Ethereum blockchain), mining attacks, and who has access to the private key of a wallet where AppCoins are stored. Aptoide is unable to assure that it can prevent such external factors from having any direct or indirect adverse impact on any of the AppCoins. Persons intending to purchase AppCoins should note that adverse events caused by such external factors may results in the loss of some or all AppCoins purchased. Such loss may be irreversible. Aptoide is not responsible for taking steps to retrieve AppCoins lost in this manner.

\medskip

\textit{Risks in purchasing AppCoins}\\
Aptoide cannot and does not guarantee or otherwise assure that there are no risks in relation to your purchase of AppCoins. The purchase of AppCoins may, depending on the manner in which the relevant purchase is effected, involve third parties or external platforms (e.g., wallets). The involvement of such parties or platforms may introduce risks that would not otherwise be present, such as misconduct or fraud by the third party, or your failure to receive AppCoins upon duly making payment because of a third-party wallet's incompatibility with AppCoins. Aptoide is not responsible for any risks arising due to the involvement of third parties, including the risk of not receiving (or subsequently losing) any or all AppCoins you attempt to (or successfully) purchase.










